### 2014-01-20 thesis/src/chapters/chapter-5-design.tex
Thesis: chapter 5

% darek
\section{Autonomic container manager}

>>>>

% darek
\section{Autonomic container manager}
It is expected that autonomic container manager supervises lifecycle of a container, modifying its properties accordingly to a current demand.

\subsection{Managed resource}
Container is an entity that provides an execution environment for an application platform. Whilst Cloud-SAP is a hypervisor agnostic, it is recommended to use operating system level virtualization technique instead of a full virtualization as a underlying mechanism for a container provisioning. Lightweight containers are more suitable for our needs especially because we rely entirely on Linux based operating system. Hence, it not necessary to use hardware-based hypervisor that supports other operating systems. Moreover, lightweight containers have been proved more effective in some scenarios: \cite{RaHiSj13}.

Container uses variety of underlying resources such as storage or network connection. However, for a simplicity, Cloud-SAP doesn't require autonomic container manager to manage them.

\subsubsection{Touchpoint}
Container's touchpoint externalises hypervisor and operating system APIs. Similarly to all touchpoints, two main parts can be distinguished:
\begin{itemize}
 \item \emph{sensors} - set of properties that expose system metrics such as CPU, memory, disk usage, network bandwidth
 \item \emph{effectors} - a collection of 'set' operations that aims to change container state: increase or decrease CPU or memory, for example. In fact, these operations directly corresponds to hypervisor capabilities.
\end{itemize}

It is highly recommended that sensors and effectors to be linked together, forming manageability capabilities. In other words, property (i.e. CPU) can be read only when it is possible to set it as well.

\subsection{Autonomic controller}
As one can see in XXX, autonomic controller has 4

\subsubsection{Monitoring}

\subsubsection{Analysis}
\subsubsection{Planning}
\subsubsection{Execution}
\subsubsection{Knowledge}

### 2014-01-20 thesis/src/chapters/chapter-adaptivity.tex
Thesis: chapter 5

\section{Introduction}
What makes a concept of an adaptivity enticing is crucial idea behind guaranteeing Quality-of-Serivce: automatization. Generally, ensuring and enforcing given quality can be seen as continuous monitoring an reacting to events when necessary. Such idea can be expressed as following IT process:

While system administrator can be directly responsible for manually performing above-mentioned steps, it is much more favourable to automatize this process leading to system self-adaptation. Not only does it lead to efficiency of an IT process but also to its effectiveness \cite{IBM06}. It is possible through:
\begin{itemize}
  \item \emph{rapid process initiation} - components auto-initiates actions based on information derived from a system
  \item \emph{reduced time and skill requirements} - automatization of IT processes makes them easier and less troublesome what is especially important for skill-intensive, error-prone and long lasting tasks
\end{itemize}

>>>>

\section{Introduction}
What makes a concept of an adaptivity enticing is crucial idea behind guaranteeing Quality-of-Serivce: automatization. Generally, ensuring and enforcing given quality can be seen as continuous monitoring and reacting to events when necessary. Such idea can be expressed as IT process shown in figure \ref{ch3:it-process}.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-3/it-process}
  \end{center}
  \caption{Exemplary IT process}
  \label{ch3:it-process}
\end{figure}

While system administrator can be directly responsible for manually performing above-mentioned steps, it is much more favourable to automatize this process leading to a system self-management or an adaptable system. Not only does it lead to efficiency of an IT process but also to its effectiveness \cite{IBM06}. It is possible through:
\begin{itemize}
  \item \emph{rapid process initiation} - components auto-initiates actions based on information derived from a system
  \item \emph{reduced time and skill requirements} - automatization of IT processes makes them easier and less troublesome what is especially important for skill-intensive, error-prone and long lasting tasks
\end{itemize}
